---
title: "Project proposal"
author: "The Zoboomafoos"
output: html_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(dplyr)
```

## 1. Data
The lemur data we found comes from the Duke Lemur Center, and was cleaned by Jesse Mostipak. The Duke Lemur Center has around 200 individual lemurs across 14 species, and it the most diverse population of lemurs outside of Madagascar which makes it a very interesting dataset to look through. There is a total of 54 different variables in the dataset and a total of 82,609 rows-each being an individual lemur that is or was living at the Duke Lemur Center. As we know the data has been cleaned already, we can tell it is tidy and well organized.

```{r add-view-data}

lemurs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-08-24/lemur_data.csv')

write_csv(lemurs, file = "../data/lemurs.csv")

glimpse(lemurs)
```

## 2. Exploratory Visualization

```{r age-offspring}
lemurs %>% 
  group_by(n_known_offspring, age_max_live_or_dead_y) %>% 
  arrange(desc(n_known_offspring))
```

This will help see if there is a connection between age and birth count

```{r graph-births}
lemurs %>% 
  ggplot(data = lemurs, mapping = aes(x = age_max_live_or_dead_y, )) +
  geom_histogram()
```

This graphs helps see what age range would be the best to pull from to get the most observations which will help create more accurate graphs and tables.

## 3. Possible question and method

Since the data set is very comprehensive we could look at the correlations between lemur traits like age and litter size. We could further stratify the data by grouping these findings by species. 

Some methods that will be good in process will be the groupby and summarize functions as well as the mean and median functions. There are a lot of observations in the data set, so constraining what we want to look at will be important. 
